---
title: "Multiple Linear Regression"
author: "Sbonelo Gumede"
date: "`r Sys.Date()`"
format: html
---

```{r setup, echo=FALSE, include=FALSE}
library("knitr")
opts_chunk$set(echo=FALSE)
```

Read the data.
```{r, echo=TRUE}
data <- read.csv(file="multreg.csv")
```

Display the data.
```{r, echo=TRUE}
kable(data) # View(data) is also appropriate.
```

Calculate the correlation of the first 5 columns. <br>
Notice that this is the correlation matrix of only the continuos variables.

```{r, echo=TRUE}
cor(data[, 1:5])
```

Fitting the linear model.<br>
Recall that the population formula is $Y = \beta_{0} + \beta_{1}*X_{1} + ... + \beta_{p}*X_{p} + e$ where e ~ N(0, $\sigma^2$). <br>
Since we are working with a sample, our formula becomes
$Y = \hat{\beta}_0 + \hat{\beta}_1*X_{1} + ... + \hat{\beta}_p*X_{p}$. <br>
In our case the model is $Y = \hat{\beta}_{0} + \hat{\beta}_{PlotSize}*X_{PlotSize} + \hat{\beta}_{FloorArea}*X_{FloorArea} + \hat{\beta}_{Trees}*X_{Trees} + \hat{\beta}_{Distance}*X_{Distance} + \hat{\beta}_{PlotSize*FloorArea}*X_{PlotSize*FloorArea}$. <br>

We want to estimate these beta coefficients. <br>
Using either the method of Odinary Least Squares or the method of Maximum likelihood we can. <br>
In R you just use the following function. <br>

```{r, echo=TRUE}
fit <- lm(Price ~ PlotSize + FloorArea + Trees + Distance + PlotSize*FloorArea,
			 data = data)
```

Now we see what the estimates of the beta coefficients are in the summary out put. <br> 
Which are significant? <br>
How do you know that? <br>

```{r, echo=TRUE}
summary(fit)
```

Now we find the 95\% confidence interval of our beta estimates. <br>
By defaults it calculates the 95\%. <br>

```{r, echo=TRUE}
confint(fit)
```

Finish off by predicting prices of houses based on our model.

```{r, echo=TRUE}
predict(fit)
```